MultiDataImportPico

### 2023-12-06 Code/MultiDataImportPico.Rmd
Fixed file path and save compressed .rds

---
title: "MultiDataImportTemplate"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","MultiCultiData")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("..","ImportedData")
#MetaCatalog <- file.path("..","PicoCatalog.csv")

Sensor <- "od-680"

#interactively set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#replaced by dynamic extraction from the first row of the AbsTime column in the datafile
#StartHour <- 7

@@

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

@@

# SensorWavebands = c(680, 720)
# SensorColours = c("red", "black")
# names(SensorColours) <- SensorWavebands
# 
# SensorColours
```

@@

gs4_deauth()

@@

Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%

  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(Catalog)

Catalog <- Catalog %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`))

@@

# List previously imported files

@@

for Project that are saved in DataIn and Previously Processed Files

```{r MultiCulti files}
MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

@@

#Run this if Run number exceeds 99.  MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'

@@

# TargetDataPlotPrelim <- 
  TargetData %>%
  filter(grepl("od-", key)) %>%
  #filter(grepl("od-sensors-", key)) %>%
  ggplot(data = .) +
  geom_point(aes(x = time, y = value, colour = as.factor(str_detect(key, "680"))), size = 0.5) +
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) + 
  #coord_cartesian(xlim = c(-5, 800)) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = c("black", "red")) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", title = "Tubes") +
  facet_grid(cols = vars(as.factor(Tube))) +
  theme_bw()

# + 
#     theme(legend.position="none")

# TargetDataPlotPrelim

#cols = vars(Filename),

#, fill = if_else(str_detect(key, "680"), "red", "black")

#
```

## Save Preliminary Plot to PlotsPath folder if desired

Generates .png for later presentation if needed.

```{r save preliminary plot as .png to folder}

 # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotPrelim",".png",sep = "")), plot = TargetDataPlotPrelim, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

@@

```{r second prelim plot}
#TargetDataPlotFacet <- 
  TargetDataMeta %>% ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

#TargetDataPlotFacet

@@

## Save second preliminary plot if desired

```{r save second preliminary plot as .png to folder}

 # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotFacet",".png",sep = "")), plot = TargetDataPlotFacet, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

@@

TargetDataMetaFilterPlot <- TargetDataMetaFilter %>% 
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
 # geom_point(aes(x = time, y = IsMovAvgOutlier680)) +
#scale_x_continuous(limits = c(0,100))+
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
 facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

TargetDataMetaFilterPlot
```

Supplementary Growth Plot
```{r, fig.height = 6, fig.width = 4}

# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time)
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   ggh4x::facet_nested(rows = vars(WL), cols = vars(Strain, Par_ue), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_both)) +
#   theme_bw()
# TargetDataMetaFilterExpandPlot
# 
# 
# 
# Par_ue.labs <- c("Growth Light Intensity: 60 µE")
# names(Par_ue.labs) <- c("60")
# WL.labs <- c("Growth Color Light: 660 nm")
# names(WL.labs) <- c("660")
# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time)
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
#   # annotate(geom = "text", x = OD680_x, y = OD680_y, label = ""~OD[680]~"", size = 4.5, colour = "darkgreen", vjust = -14.5, hjust = 2.5) +
#   # annotate(geom = "text", x = OD720_x, y = OD720_y, label = ""~OD[720]~"", size = 4.5, colour = "blue", vjust = -20, hjust = 2.5) +
# theme_bw() +
# theme(strip.text.x = element_text(size = 12),
#       strip.text.y = element_text(size = 12),
#       #strip.background = element_rect(color="black", size=0.5, linetype="solid"),
#       axis.text = element_text(size = 12),
#       axis.title = element_text(size = 12))
# 
# # theme(strip.background = element_rect(color="black", size=1.5, linetype="solid"))
# 
# TargetDataMetaFilterExpandPlot
# # grob <- grobTree(textGrob("Scatter plot", x=0.1,  y=0.95, hjust=0,
# #   gp=gpar(col="red", fontsize=13, fontface="italic")))
# #annotation_custom(grob)+facet_wrap(~cyl, scales="free")
# 
# 
# 
# #labelling dynamically offset from data traces.
# #use 'median' for 'x' and OD680 + offset for 'y'
# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time) 
# Light_x = max(TargetDataMetaFilter$time) - 200
# 
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# 
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# 
# Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1
# 
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), size = 0.1, colour = "darkgreen") +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   
#   # scale_x_continuous(breaks=seq(0, 250, by = 50)) +
#   # coord_cartesian(xlim = c(0, 250)) +
#   
#   scale_colour_manual(values = MCMIXColours) +
#   geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
#   #geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#   #geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   # coord_cartesian(xlim = c(0, 800)) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   #facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
#   #annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkgreen") +
#   #annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "blue") +
#   #annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
#   theme_bw() +
#   theme(strip.text.x = element_text(size = 12),
#       strip.text.y = element_text(size = 12),
#       axis.text = element_text(size = 12),
#       axis.title = element_text(size = 12))
#   labs(colour = "Actinic PAR (nm)")
# 
# TargetDataMetaFilterExpandPlot

@@

TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  # coord_cartesian(xlim = c(0, 800)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

TargetDataMetaFilterExpandPlot

# TargetDataPlotFacet <- TargetDataMeta %>% ggplot() +
#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
#   scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density 680nm (OD680)", x = "Elapsed Time (h)") +
#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Par_ue),Strain, as.factor(Tube))) +
#   theme_bw() +  
#   labs(colour = "Actinic PAR (nm)")

@@

## Save filtered preliminary plot if desired

```{r save filtered preliminary plot as .png to folder}
# 
#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterPlot",".png",sep = "")), plot = TargetDataMetaFilterPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# # 
#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterExpandPlot",".png",sep = "")), plot = TargetDataMetaFilterExpandPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

@@

```{r save Rds of imported data}
saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
```

>>>>

---
title: "MultiDataImportPico"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCulti")
DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")

@@

#set Photobiology colors
```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

@@

@@

# gs4_deauth()

@@

# Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%

  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
#   drop_na(WL) %>%
#   mutate(WL = unlist(WL))
# 
# as.data.frame(Catalog)
# 
# Catalog <- Catalog %>%
#    mutate(ExpDate = ymd(ExpDate),
#           ExpEndDate = ymd_hms(`ExpEndDate`))

@@

```{r read locally stored metadata from rds}

CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))

# List previously imported MultiCulti files

@@

for Project that are saved in DataIn

```{r MultiCulti files}

MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

@@

@@

  TargetData %>%
  filter(grepl("od-", key)) %>%
  #filter(grepl("od-sensors-", key)) %>%
  ggplot(data = .) +
  geom_point(aes(x = time, y = value, colour = as.factor(str_detect(key, "680"))), size = 0.5) +
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) + 
  #coord_cartesian(xlim = c(-5, 800)) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = c("black", "red")) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", title = "Tubes") +
  facet_grid(cols = vars(as.factor(Tube))) +
  theme_bw()

@@

```{r second prelim plot}

  TargetDataMeta %>% ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

@@

@@

TargetDataMetaFilter %>% 
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
 # geom_point(aes(x = time, y = IsMovAvgOutlier680)) +
#scale_x_continuous(limits = c(0,100))+
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
 facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

@@

TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  # coord_cartesian(xlim = c(0, 800)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

@@

@@

```{r save Rds of imported data}
saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = "xz", refhook = NULL)
```
